Taxonomic bias can create spurious results in microbiome differential-abundance analyses unless it is properly accounted for

### 2021-05-12 index.Rmd
Improve pdf formatting
- Migrate all output options to the YAML block of index.Rmd to ensure
  all options are specified correctly and don't conflict; see links
  below
- Adjust pandoc options for pdf output

https://github.com/rstudio/bookdown/issues/918
https://github.com/rstudio/bookdown/issues/921

---
title: "Taxonomic bias can create spurious results in microbiome differential-abundance analyses unless it is properly accounted for"
author:
  - Michael R. McLaren^[North Carolina State University; send correspondence to m.mclaren42@gmail.com]
  - Karen G. Lloyd^[University of Tennessee]
  - Benjamin J. Callahan^[North Carolina State University]
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [main.bib, packages.bib]
biblio-style: apalike
link-citations: yes
# description:
github-repo: mikemc/bda-theory
---

>>>>

---
title: "Taxonomic bias can create spurious results in microbiome differential-abundance analyses unless it is properly accounted for"
author:
  - Michael R. McLaren^[North Carolina State University; send correspondence to m.mclaren42@gmail.com]
  - Karen G. Lloyd^[University of Tennessee]
  - Benjamin J. Callahan^[North Carolina State University]
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
bibliography: [main.bib, packages.bib]
biblio-style: apalike
link-citations: yes
# description:
# For pandoc latex processing
documentclass: article
geometry:
  - top=1in
  - bottom=1in
  - left=1.5in
  - right=1.5in
output:
  bookdown::gitbook:
    css: style.css
    number_sections: true
    config:
      sharing:
        facebook: no
        github: yes
        twitter: no
        linkedin: no
        weibo: no
        instapaper: no
        vk: no
        all: ['facebook', 'twitter', 'linkedin', 'weibo', 'instapaper']
  bookdown::pdf_book:
    includes:
      in_header: latex/preamble.tex
    keep_tex: true
    dev: "pdf"
    papersize: letter
    toc_depth: 2
    toc_unnumbered: yes
    toc_appendix: yes
---
